Global adjoint tomography -- Model GLAD-M25\footnote{This paper is dedicated to Dimitri Komatitsch, computational geophysicist extraordinaire, who passed away unexpectedly shortly before its submission.}

### 2019-02-21 main.tex
Updates from Overleaf

Global adjoint tomography has a well-defined but complex workflow with multiple stages.
% including numerical simulations of synthetic seismograms (forward simulations) for all events,
% pre-processing of seismic data, making measurements, data assimilation, Fr\'echet derivative
% calculations (adjoint simulations), and post-processing of the gradient for quasi-Newton model
% updates.
It is essential to optimize, automate, and harden the entire process using workflow management tools, especially with large data sets.
For each iteration,
1,480 forward and adjoint simulations need to be performed,
generating a few Petabytes of wavefield files for the parsimonious-storage kernel calculation algorithm of~\cite{KoXiBoPeSaLiTr16}, and consuming 16~million OLCF node hours.
How to deal with hardware failures during this process is critical
to prevent contamination of the inversion results.
For these reasons, we use EnTK as our
workflow management engine~\citep{EnTK2017}.
This workflow engine can automatically detected job failures,
both from the high-performance computing (HPC) system and via user-defined functions.
This facilitates tracking of tasks and semi-automatic job resubmission if necessary.

@@

There are more than ten stages in the adjoint tomography workflow,
and each stage involves thousands of small tasks.
For every model iteration,
we performed up to 1,480 forward and adjoint simulations, each involving hundreds of
compute cores and graphics cards, as well as heavy I/O.
The workflow is prone to human error and hardware failure, making it fragile~~\citep{Lefebvre2018}.
For these reasons, we hardened the workflow by taking advantage of modern
workflow management software.
We selected EnTK as our
workflow management engine~\citep{EnTK2017}, and developed complementary seismic tomography
workflow tools.
The workflow engine can automatically detected job failures both from the
HPC system and via user-defined functions. This enables us to keep track of
all tasks and semi-automatically resubmit jobs if necessary.
Given that most HPC system time is spent waiting in the job queue, automatic
failure detection and relaunching greatly shortens the overall time to solution.

>>>>

Global adjoint tomography has a well-defined but complex workflow with multiple stages.
% including numerical simulations of synthetic seismograms (forward simulations) for all events,
% pre-processing of seismic data, making measurements, data assimilation, Fr\'echet derivative
% calculations (adjoint simulations), and post-processing of the gradient for quasi-Newton model
% updates.
It is essential to optimize, automate, and harden the entire process using workflow management tools, especially with large data sets.
For each iteration,
1,480 forward and adjoint simulations need to be performed,
generating a few Petabytes of wavefield files for the parsimonious-storage kernel calculation algorithm of~\cite{KoXiBoPeSaLiTr16}, and consuming 16~million OLCF node hours.
How to deal with hardware failures during this process is critical
to prevent contamination of the inversion results.
For these reasons, we are in the process of using EnTK as our
workflow management engine~\citep{EnTK2017}.
This workflow engine can automatically detected job failures,
both from the high-performance computing (HPC) system and via user-defined functions.
This facilitates tracking of tasks and semi-automatic job resubmission if necessary.

@@

There are more than ten stages in the adjoint tomography workflow,
and each stage involves thousands of small tasks.
For every model iteration,
we performed up to 1,480 forward and adjoint simulations, each involving hundreds of
compute cores and graphics cards, as well as heavy I/O.
The workflow is prone to human error and hardware failure, making it fragile~~\citep{Lefebvre2018}.
For these reasons, we hardened the workflow by taking advantage of modern
workflow management software.
We have selected EnTK as our
workflow management engine~\citep{EnTK2017}, and developed complementary seismic tomography
workflow tools.
The workflow engine can automatically detected job failures both from the
HPC system and via user-defined functions. This enables us to keep track of
all tasks and semi-automatically resubmit jobs if necessary.
Given that most HPC system time is spent waiting in the job queue, automatic
failure detection and relaunching greatly shortens the overall time to solution.
